---
title: "Ast2: The Dark Forest"
date: "2024-02-12"
output: "html_document"
---

# Electricity Consumption

## Access the data

[Data source](https://weather.gc.ca/city/pages/bc-45_metric_e.html)

Hourly data interval:

```sh
for year in `seq 1998 2008`;do for month in `seq 1 12`;do wget --content-disposition "https://climate.weather.gc.ca/climate_data/bulk_data_e.html?format=csv&stationID=1706&Year=${year}&Month=${month}&Day=14&timeframe=1&submit= Download+Data" ;done;done
```

Note: to download the hourly data in UTC rather than LTC, please add &time=utc after format=csv in the wget statement

Daily data interval:

```sh
for year in `seq 1998 2008`;do for month in `seq 1 1`;do wget --content-disposition "https://climate.weather.gc.ca/climate_data/bulk_data_e.html?format=csv&stationID=1706&Year=${year}&Month=${month}&Day=14&timeframe=2&submit= Download+Data" ;done;done
```

Monthly data interval (specific time period):

```sh
for year in `seq 1998 2008`;do for month in `seq 1 12`;do wget --content-disposition "https://climate.weather.gc.ca/climate_data/bulk_data_e.html?format=csv&stationID=1706&Year=${year}&Month=${month}&Day=14&timeframe=3&submit= Download+Data" ;done;done
```

Monthly data interval (station complete history):

```sh
for year in `seq 1998 2008`;do for month in `seq 1 1`;do wget --content-disposition "https://climate.weather.gc.ca/climate_data/bulk_data_e.html?format=csv&stationID=1706&Year=${year}&Month=${month}&Day=14&timeframe=3&submit= Download+Data" ;done;done
```

## The modified command

```sh
for year in `seq 2021 2024`;
	do for month in `seq 1 1`;
		do 
		wget --content-disposition "https://climate.weather.gc.ca/climate_data/bulk_data_e.html?format=csv&stationID=51423&Year=${year}&Month=${month}&Day=14&timeframe=2&submit= Download+Data" ;
	done;
done

# "KAMLOOPS A","BRITISH COLUMBIA","1163781","51423","71887","YKA","50.7","-120.45","504209000","-1202655000","345.3","2013","2023","2013","2023","2013","2023","",""

```

```{r results=FALSE}
ECON_DATA_SOURCE_PATH = "data/consumption_20240208.csv"
TEMP_DATA_SOURCE_PATH = "data/temp.csv"
ECON = read.csv(ECON_DATA_SOURCE_PATH)
TEMP = read.csv(TEMP_DATA_SOURCE_PATH)
# Check the number of NAs, The header names are kept original.
# sum(sapply(TEMP$Mean.Temp...C., function(x) sum(is.na(x))))
# sum(sapply(ECON$Net.Consumption..kWh., function(x) sum(is.na(x))))
TEMP$Date
ECON$Date = sapply(ECON$Date_interval, function(x) substring(x,first=1 ,last=10))
DATA_MERGED = merge(ECON, TEMP, by = "Date")
DATA_MERGED
```

```{r}
lmod1 <- lm(DATA_MERGED$Econ_kWh ~ DATA_MERGED$Mean.Temp)

plot(DATA_MERGED$Econ_kWh ~ DATA_MERGED$Mean.Temp, xlab = "Temperature (°C)", ylab = "Electricity Consumption (kWh)")
abline(lmod1)

mod1fit = function(x){lmod1$coefficients[1]+lmod1$coefficients[2]*x}
temperature <- c(-40, -20, 0, 20, 40)
mod1estimate = data.frame(Mean.Temp = temperature, Econ_kWh = mod1fit(temperature))
```

Same thing using `ggplot2`

```{r}
library(ggplot2)
ggplot(data = DATA_MERGED, aes(x = Mean.Temp, y = Econ_kWh)) +
  xlim(-40,40)+
  geom_point(color = "blue") +  # scatter plot of data points
  #geom_smooth(method = "lm", se = FALSE, color = "red") +  # linear regression line
  stat_function(fun=mod1fit)+
  geom_point(data=mod1estimate, color = "red", size = 4, shape = 1, )+
  geom_point(data=mod1estimate, color = "orange")+
  labs(x = "Temperature (°C)", 
       y = "Electricity Consumption (kWh)") +
  theme_minimal()
```


Using the following linear regression model:

$$
\mathbf{y}_{econ} = -0.19582 \mathbf{x}_{temp} + 15.42925
$$

Where $\mathbf{x}_{temp}$ is the outside temperature (in °C), and $\mathbf{y}_{econ}$ is the electricity consumption (in kWh). Our conclusion is: 


The Electricity consumption would decrease when the outside temperature increase.

```{r}
lmod1$coefficients
lmod1 |> summary()

mod1fit(temperature)


```

From the scatterplot, we can see a "concave" pattern, showing strong non-linearality as the electricity consumption first decrease then increase when the temperature goes from -40 °C to 40 °C.

```{r}
library(ggplot2)
DATA_MERGED["Mean.Temp.Squared"] = (DATA_MERGED$Mean.Temp)^2
lmod2 <- lm(DATA_MERGED$Econ_kWh ~ DATA_MERGED$Mean.Temp + DATA_MERGED$Mean.Temp.Squared)

mod2fit <- function(x){lmod2$coefficients[1]+lmod2$coefficients[2]*x+lmod2$coefficients[3]*x^2}

mod2estimate = data.frame(Mean.Temp = temperature, Econ_kWh = mod2fit(temperature))

mod2estimate
#plot(DATA_MERGED$Econ_kWh ~ DATA_MERGED$Mean.Temp, xlab = "Temperature (°C)", ylab = "Electricity Consumption (kWh)")
#lines(DATA_MERGED$Mean.Temp[ix],predict(lmod2)[ix], col='red')
```

\begin{tabular}{r|r}
\hline
Mean.Temp & Econ\_kWh\\
\hline
-40 & 87.10993\\
\hline
-20 & 38.67409\\
\hline
0 & 13.77471\\
\hline
20 & 12.41178\\
\hline
40 & 34.58531\\
\hline
\end{tabular}


```{r results='asis'}
knitr::kable(mod2estimate, format = "latex")
```



```{r}
ggplot(data = DATA_MERGED, aes(x = Mean.Temp, y = Econ_kWh)) +
  xlim(-40,40)+
  geom_point(color = "blue") +  # scatter plot of data points
  #geom_smooth(method = "lm", se = TRUE, color = "red") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  stat_function(fun=mod2fit)+
  labs(x = "Temperature (°C)", 
       y = "Electricity Consumption (kWh)") +
  geom_point(data=mod2estimate, color = "red", size = 4, shape = 1, )+
  geom_point(data=mod2estimate, color = "orange")+
  theme_minimal()
```

```{r}
plants = read.csv("plants.csv")

lm_model <- lm(height ~ width, data = plants)

summary(lm_model)

plot(plants$width, plants$height, xlab = "Width of Plants", ylab = "Height of Plants", main = "Relationship between Plants Height and Width")
abline(lm_model, col = "red")  # Overlay regression line
```

Ignoring spicies

```{r}
ggplot(data = plants, aes(x = width, y = height)) +
  geom_point(color = "blue") +  # scatter plot of data points
  geom_smooth(method = "lm", se = F, color = "black") +  # linear regression line
  #geom_point(data = data.frame(width=plants$width, height=predict(lm_model)))+
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
```

Not Ignoring species

```{r}
#Specie A
ggplot(data = subset(plants, species == "A") , aes(x = width, y = height)) +
  geom_point(color = "blue") +  # scatter plot of data points
  geom_smooth(method = "lm", se = F, color = "black") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
```

```{r}
#Specie B
ggplot(data = subset(plants, species == "B") , aes(x = width, y = height)) +
  geom_point(color = "blue") +  # scatter plot of data points
  geom_smooth(method = "lm", se = F, color = "black") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
```

```{r}
#Specie C
ggplot(data = subset(plants, species == "C") , aes(x = width, y = height)) +
  geom_point(color = "blue") +  # scatter plot of data points
  geom_smooth(method = "lm", se = F, color = "black") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
```

```{r}
#Specie D
ggplot(data = subset(plants, species == "D") , aes(x = width, y = height)) +
  geom_point(color = "blue") +  # scatter plot of data points
  geom_smooth(method = "lm", se = F, color = "black") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
```

```{r}
#Specie E
ggplot(data = subset(plants, species == "E") , aes(x = width, y = height)) +
  geom_point(color = "blue") +  # scatter plot of data points
  geom_smooth(method = "lm", se = F, color = "black") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
```

```{r}
ggplot(data = plants  , aes(x = width, y = height)) +
  geom_point(data = subset(plants, species == "E"), color = "navy", shape = 1) +  # E
  geom_smooth(data =  subset(plants, species == "E"), method = "lm", se = F, color = "black") +  # linear regression line
  geom_point(data = subset(plants, species == "D"), color = "blue", shape = 2) +  # E
  geom_smooth(data =  subset(plants, species == "D"), method = "lm", se = F, color = "black") +  # linear regression line
  geom_point(data = subset(plants, species == "C"), color = "mediumslateblue", shape = 3) +  # E
  geom_smooth(data =  subset(plants, species == "C"), method = "lm", se = F, color = "black") +  # linear regression line
  geom_point(data = subset(plants, species == "B"), color = "cornflowerblue", shape = 4) +  # E
  geom_smooth(data =  subset(plants, species == "B"), method = "lm", se = F, color = "black") +  # linear regression line
  geom_point(data = subset(plants, species == "A"), color = "blueviolet", shape = 5) +  # E
  geom_smooth(data =  subset(plants, species == "A"), method = "lm", se = F, color = "black") +  # linear regression line
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = TRUE, color = "green") +  # polynomial fit curve (quadratic)
  labs(x = "Width of Plants", 
       y = "Height of Plants") +
  theme_minimal()
  choose(6,3)
```

```{r}
qqnorm(residuals(lm_model))
lm_model
summary(lm_model)

lm_modelA <- lm(height ~ width, subset(plants, species == "A"))
lm_modelB <- lm(height ~ width, subset(plants, species == "B"))
lm_modelC <- lm(height ~ width, subset(plants, species == "C"))
lm_modelD <- lm(height ~ width, subset(plants, species == "D"))
lm_modelE <- lm(height ~ width, subset(plants, species == "E"))
summary(lm_modelE)
```



